### 2025-11-23 tex/manuscript.tex
Fix: Typo
Fix: Numerous typos, GE-01 seat ordering
Original manuscript

% bibliography-related packages
\usepackage[superscript]{cite}
\bibliographystyle{unsrt}

@@

For the 3 elections after 8th March 2008 (Figure \ref{fig:federal_coverage}), official results are available digitally via the aforementioned dashboard, in a manner that enabled us to directly scrape the results, albeit with the trial and error generally required for frontend web scraping. Where unavailable (all 13 elections prior to and including the 2008 federal general election), we manually (i.e.\ by hand) digitised the data from the aforementioned post-election reports and gazetted results. We made a deliberate methodological choice to avoid the use of optical character recognition (OCR) and PDF parsing tools after initial experimentation revealed an average error rate of approximately 10\%, primarily due to frequent changes in formatting and layout, even within the same document. We considered this to be unacceptably high for a resource intended to serve as a single source of truth, especially since . Moreover, the downstream process of error detection and correction proved to be more time-consuming and error-prone than simply transcribing the data by hand, especially given the relatively manageable size of this data (\TOTALBALLOTS\space ballots across \TOTALCONTESTS\space electoral contests).

@@

\textbf{Constituencies.}
We deliberately avoided assigning UIDs to constituencies. Instead, we rely on the intrinsic uniqueness of the \texttt{date-state-constituency} combination, which guarantees that each contest is uniquely identifiable within its context (since no two constituencies within the same state can have the same name in the same election). A left join on these three fields suffices to generate a lookup table via which additional data can be merged. To aid users in harmonising constituencies across elections, we provide a field called \texttt{area\_name}, which standardises name changes and spelling variations across time. Examples include:
\begin{align*}
\text{Temerluh} &\rightarrow \space \text{Temerloh}\\ 
\text{Teluk Anson} &\rightarrow \space \text{Teluk Intan}\\
\text{Bagan Datoh} \rightarrow \space \text{Bagan}&\text{ }\text{Datok} \rightarrow \space \text{Bagan Datuk}
\end{align*}
We do not currently implement harmonisation for changes involving boundary adjustments or the creation of new constituencies. For example, although the seat of Bayan Baru in Penang was carved out of Balik Pulau, we do not merge or tag these together because Balik Pulau remains an active seat name today, and such harmonisation would require subjective judgment. Our aim is to provide a flexible foundation that allows users to apply their own harmonisation strategies according to their specific research needs.

@@

For numerical data, the way in which Malaysia reports election results makes a unique form of validation possible. First, we define the following variables:
\begin{align*}
	I &= \text{Ballots Issued} \\
	U &= \text{Unreturned Ballots} \\
	R &= \text{Votes Rejected} \\
	V_i &= \text{Valid Votes for Candidate } i
\end{align*}
For a given contest involving $N$ candidates, the following relationship must hold:
\begin{align}
	\label{eq:validation}
	I - U - R = \sum_{i=1}^{N} V_i
\end{align}
In plain language, the implied number of valid votes must be equal to the sum of votes received by all candidates. Because $I$, $U$, $R$, and $V_i$ are (and have been) reported separately in all historical election reports and gazetted results, we can leverage this relationship as an almost-foolproof way to validate the accuracy of our manual data entry process. For transparency, we detected and corrected errors for 82 out of \TOTALCONTESTS\space contests, implying an error rate of 0.84\%, which is significantly lower than the 10\% error rate we encountered in our initial OCR experiments. Importantly, these errors are detectable and fixable, and come without the additional overhead of correcting errors in text data; our familiarity with local geography, politicians, and culture enabled us to transcribe text data rapidly and accurately.

@@

>>>>

% bibliography-related packages
\usepackage[superscript]{cite}
\bibliographystyle{unsrt}
\usepackage{filecontents}

@@

For the 3 elections after 8th March 2008 (Figure \ref{fig:federal_coverage}), official results are available digitally via the aforementioned dashboard, in a manner that enabled us to directly scrape the results, albeit with the trial and error generally required for frontend web scraping. Where unavailable (all 13 elections prior to and including the 2008 federal general election), we manually (i.e.\ by hand) digitised the data from the aforementioned post-election reports and gazetted results. We made a deliberate methodological choice to avoid the use of optical character recognition (OCR) and PDF parsing tools after initial experimentation revealed an average error rate of approximately 10\%, primarily due to frequent changes in formatting and layout, even within the same document. We considered this to be unacceptably high for a resource intended to serve as a single source of truth. Moreover, the downstream process of error detection and correction proved to be more time-consuming and error-prone than simply transcribing the data by hand, especially given the relatively manageable size of this data (\TOTALBALLOTS\space ballots across \TOTALCONTESTS\space electoral contests).

@@

\textbf{Constituencies.}
We deliberately avoided assigning UIDs to constituencies. Instead, we rely on the intrinsic uniqueness of the \texttt{date-state-constituency} combination, which guarantees that each contest is uniquely identifiable within its context (since no two constituencies within the same state can have the same name in the same election). A left join on these three fields suffices to generate a lookup table via which additional data can be merged. To aid users in harmonising constituencies across elections, we provide a field called \texttt{area\_name}, which standardises name changes and spelling variations across time. Examples include:
\begin{align*}
	\text{Temerluh}                                    & \rightarrow \space \text{Temerloh}                         \\
	\text{Telok Anson}                                 & \rightarrow \space \text{Teluk Intan}                      \\
	\text{Bagan Datoh} \rightarrow \space \text{Bagan} & \text{ }\text{Datok} \rightarrow \space \text{Bagan Datuk}
\end{align*}
We do not currently implement harmonisation for changes involving boundary adjustments or the creation of new constituencies. For example, although the seat of Bayan Baru in Penang was carved out of Balik Pulau, we do not merge or tag these together because Balik Pulau remains an active seat name today, and such harmonisation would require subjective judgment. Our aim is to provide a flexible foundation that allows users to apply their own harmonisation strategies according to their specific research needs.

@@

For numerical data, the way in which Malaysia reports election results makes a unique form of validation possible. First, we define the following variables:
\begin{align*}
	I   & = \text{Ballots Issued}               \\
	U   & = \text{Unreturned Ballots}           \\
	R   & = \text{Votes Rejected}               \\
	V_i & = \text{Valid Votes for Candidate } i
\end{align*}
For a given contest involving $N$ candidates, the following relationship must hold:
\begin{align}
	\label{eq:validation}
	I - U - R = \sum_{i=1}^{N} V_i
\end{align}
In plain language, the implied number of valid votes must be equal to the sum of votes received by all candidates. Because $I$, $U$, $R$, and $V_i$ are (and have been) reported separately in all historical election reports and gazetted results, we can leverage this relationship as an almost-foolproof way to validate the accuracy of our manual data entry process. For transparency, we detected and corrected errors for 82 out of \TOTALCONTESTS\space contests, implying an error rate of 0.84\%, which is significantly lower than the 10\% error rate we encountered in our initial OCR experiments. Importantly, these errors are detectable and fixable, and come without the additional overhead of correcting errors in text data; our familiarity with local geography, politicians, and culture enabled us to transcribe text data rapidly and accurately.

@@

\begin{filecontents*}{mybib.bib}

	@misc{mysprsemak,
		title        = {{MySPR Semak}} ,
		author       = {Election Commission},
		year         = {2025},
		url          = {https://mysprsemak.spr.gov.my/semakan/keputusan/pru},
		note         = {Accessed: 2025-05-05}
	}

	@misc{lompub,
		title        = {{Federal Legislation: P.U.(B)}},
		author       = {Attorney General's Chambers of Malaysia},
		year         = {2025},
		url          = {https://lom.agc.gov.my/subsid.php?type=pub},
		note         = {Accessed: 2025-05-05}
	}

	@misc{clea,
		title        = {Constituency-Level Elections Archive},
		author       = {Kollman, Ken and Hicken, Allen and Caramani, Daniele and Backer, David and Lublin, David},
		year         = {2024},
		url          = {http://www.electiondataarchive.org},
		note         = {Accessed: 2025-05-05}
	}

	@article{icoma2023urnout,
		title={The Global Dataset on Turnout {(GD-Turnout)}},
		author={i Coma, Ferran Mart{\'\i}nez and Van De Maele, Diego Leiva},
		journal={Electoral Studies},
		volume={86},
		pages={102681},
		year={2023},
		publisher={Elsevier}
	}

	@article{norris2014integrity,
		title={Measuring electoral integrity around the world: A new dataset},
		author={Norris, Pippa and Frank, Richard W and i Coma, Ferran Mart{\'\i}nez},
		journal={PS: Political Science \& Politics},
		volume={47},
		number={4},
		pages={789--798},
		year={2014},
		publisher={Cambridge University Press}
	}

	@misc{undiinfo,
		title        = {undi.info},
		author       = {MalaysiaKini},
		year         = {2025},
		url          = {\url{https://citethis.link/meco1-undi}},
		note         = {Accessed: 2025-05-05}
	}

	@misc{ge15sinar,
		title        = {{GE15 Open Data}},
		author       = {Sinar Project},
		year         = {2025},
		url          = {\url{https://citethis.link/meco1-sinar}},
		note         = {Accessed: 2025-05-05}
	}

	@misc{tindakgithub,
		title        = {Historical Election Results},
		author       = {{Tindak Malaysia}},
		year         = {2025},
		howpublished = {\url{https://citethis.link/meco1-tindak}},
		note         = {Accessed: 2025-05-05}
	}

	@article{perez2021spanish,
		title={Spanish electoral archive. {SEA} database},
		author={P{\'e}rez, Virgilio and Aybar, Cristina and Pav{\'\i}a, Jose M},
		journal={Scientific Data},
		volume={8},
		number={1},
		pages={193},
		year={2021},
		publisher={Nature Publishing Group UK London}
	}

	@article{baltz2022american,
		title={{American} election results at the precinct level},
		author={Baltz, Samuel and Agadjanian, Alexander and Chin, Declan and Curiel, John and DeLuca, Kevin and Dunham, James and Miranda, Jennifer and Phillips, Connor Halloran and Uhlman, Annabel and Wimpy, Cameron and others},
		journal={Scientific Data},
		volume={9},
		number={1},
		pages={651},
		year={2022},
		publisher={Nature Publishing Group UK London}
	}

	@article{de2023american,
		title={{American} local government elections database},
		author={de Benedictis-Kessner, Justin and Lee, Diana Da In and Velez, Yamil R and Warshaw, Christopher},
		journal={Scientific Data},
		volume={10},
		number={1},
		pages={912},
		year={2023},
		publisher={Nature Publishing Group UK London}
	}

	@article{heddesheimer2025gerda,
		title={{GERDA}: The {German} Election Database},
		author={Heddesheimer, Vincent and Hilbig, Hanno and Sichart, Florian and Wiedemann, Andreas},
		journal={Scientific Data},
		volume={12},
		number={1},
		pages={618},
		year={2025},
		publisher={Nature Publishing Group UK London}
	}

	@article{calderon2025electoral,
	title={Electoral precinct-level database for {Mexican} municipal elections},
	author={Calder{\'o}n-Hern{\'a}ndez, Bruno and Larreguy, Horacio and Marshall, John and P{\'e}rez-Castellanos, Jos{\'e} Luis},
	journal={Scientific Data},
	volume={12},
	number={1},
	pages={582},
	year={2025},
	publisher={Nature Publishing Group UK London}
	}

	@article{jensenius2017studying,
	title={Studying {Indian} politics with large-scale data: {Indian} election data 1961--today},
	author={Jensenius, Francesca R and Verniers, Gilles},
	journal={Studies in Indian Politics},
	volume={5},
	number={2},
	pages={269--275},
	year={2017},
	publisher={SAGE Publications Sage India: New Delhi, India}
	}

	@book{ge00report,
		title     = {Report on the First Election of Members to the Legislative Council of the Federation of Malaya},
		author    = {T. E. Smith},
		year      = {1955},
		publisher = {Supervisor of Elections},
	}

	@book{ge01report,
		title     = {Report on the Parliamentary and State Elections 1959},
		author    = {Election Commission},
		year      = {1959},
		publisher = {Election Commission of the Federation of Malaya},
	}

	@book{ge02report,
		title     = {Report on the Parliamentary (Dewan Ra'ayat) and State Legislative Assembly General Elections, 1964 of the States of Malaya},
		author    = {Election Commission},
		year      = {1964},
		publisher = {Election Commission of the Federation of Malaya},
	}
	@book{ge03report,
		title     = {Report on the Parliamentary (Dewan Ra'ayat) and State Legislative Assembly General Elections 1969 of the States of Malaya, Sabah and Sarawak},
		author    = {Election Commission},
		year      = {1971},
		publisher = {Election Commission of Malaysia},
	}

	@book{ge04report,
		title     = {Report on the Parliamentary (Dewan Rakyat) and State Legislative Assembly General Elections 1974 of the States of Malaya and Sarawak},
		author    = {Election Commission},
		year      = {1974},
		publisher = {Election Commission of Malaysia},
	}

	@book{ge05report,
		title     = {Report on the General Elections to the House of Representatives and the State Legislative Assemblies Other Than the State Legislative Assemblies of Kelantan, Sabah and Sarawak 1978},
		author    = {Election Commission},
		year      = {1978},
		publisher = {Election Commission of Malaysia},
	}

	@book{ge06report,
		title     = {Report on the Malaysian General Elections 1982},
		author    = {Election Commission},
		year      = {1982},
		publisher = {Election Commission of Malaysia},
	}

	@book{ge07report,
		title     = {Report on the Malaysian General Elections 1986},
		author    = {Election Commission},
		year      = {1986},
		publisher = {Election Commission of Malaysia},
	}

	@book{ge08report,
		title     = {Report on the Malaysian General Elections 1990},
		author    = {Election Commission},
		year      = {1990},
		publisher = {Election Commission of Malaysia},
	}

	@book{ge09report,
		title     = {Report of the General Election Malaysia 1995},
		author    = {Election Commission},
		year      = {1995},
		publisher = {Election Commission of Malaysia},
	}

	@book{ge10report,
		title     = {Report of the General Election Malaysia 1999},
		author    = {Election Commission},
		year      = {1999},
		publisher = {Election Commission of Malaysia},
	}

	@book{ge11report,
		title     = {Report of the General Election Malaysia 2004},
		author    = {Election Commission},
		year      = {2004},
		publisher = {Election Commission of Malaysia},
	}

	@book{ge12report,
		title     = {Report of the General Election Malaysia 2008},
		author    = {Election Commission},
		year      = {2008},
		publisher = {Election Commission of Malaysia},
	}

	@book{ge13report,
		title     = {Report of the General Election Malaysia 2013},
		author    = {Election Commission},
		year      = {2013},
		publisher = {Election Commission of Malaysia},
	}

	@book{sabah1967report,
		title     = {Report on the State Legislative Assembly General Election 1967 of the State of Sabah},
		author    = {Election Commission},
		year      = {1967},
		publisher = {Election Commission of Malaysia},
	}

	@book{sabah1971report,
		title     = {Report on the State Legislative Assembly General Election 1971 of the State of Sabah},
		author    = {Election Commission},
		year      = {1971},
		publisher = {Election Commission of Malaysia},
	}

	@book{sabah1976report,
		title     = {Report on the State Legislative Assembly General Election 1976 of the State of Sabah},
		author    = {Election Commission},
		year      = {1976},
		publisher = {Election Commission of Malaysia},
	}

	@book{kelantan1978report,
		title     = {Report on the State Legislative Assembly General Election 1978 of the State of Kelantan},
		author    = {Election Commission},
		year      = {1978},
		publisher = {Election Commission of Malaysia},
	}

	@book{sarawak1979report,
		title     = {Report on the State Legislative Assembly General Election 1979 of the State of Sarawak},
		author    = {Election Commission},
		year      = {1979},
		publisher = {Election Commission of Malaysia},
	}

	@book{sabah1981report,
		title     = {Report on the State Legislative Assembly General Election 1981 of the State of Sabah},
		author    = {Election Commission},
		year      = {1981},
		publisher = {Election Commission of Malaysia},
	}

	@book{sarawak1983report,
		title     = {Report on the State Legislative Assembly General Election 1983 of the State of Sarawak},
		author    = {Election Commission},
		year      = {1983},
		publisher = {Election Commission of Malaysia},
	}

	@book{sabah1985report,
		title     = {Report on the State Legislative Assembly General Election 1985 of the State of Sabah},
		author    = {Election Commission},
		year      = {1985},
		publisher = {Election Commission of Malaysia},
	}

	@book{sabah1986report,
		title     = {Report on the State Legislative Assembly General Election 1986 of the State of Sabah},
		author    = {Election Commission},
		year      = {1986},
		publisher = {Election Commission of Malaysia},
	}

	@book{sarawak1987report,
		title     = {Report on the State Legislative Assembly General Election 1987 of the State of Sarawak},
		author    = {Election Commission},
		year      = {1987},
		publisher = {Election Commission of Malaysia},
	}

	@book{sabah1990report,
		title     = {Report on the State Legislative Assembly General Election 1990 of the State of Sabah},
		author    = {Election Commission},
		year      = {1990},
		publisher = {Election Commission of Malaysia},
	}

	@book{sarawak1991report,
		title     = {Report on the State Legislative Assembly General Election 1991 of the State of Sarawak},
		author    = {Election Commission},
		year      = {1991},
		publisher = {Election Commission of Malaysia},
	}

	@book{sabah1994report,
		title     = {Report on the State Legislative Assembly General Election 1994 of the State of Sabah},
		author    = {Election Commission},
		year      = {1994},
		publisher = {Election Commission of Malaysia},
	}

	@book{sarawak1996report,
		title     = {Report on the State Legislative Assembly General Election 1996 of the State of Sarawak},
		author    = {Election Commission},
		year      = {1996},
		publisher = {Election Commission of Malaysia},
	}

	@book{sabah1999report,
		title     = {Report on the State Legislative Assembly General Election 1999 of the State of Sabah},
		author    = {Election Commission},
		year      = {1999},
		publisher = {Election Commission of Malaysia},
	}

	@book{sarawak2001report,
		title     = {Report on the State Legislative Assembly General Election 2001 of the State of Sarawak},
		author    = {Election Commission},
		year      = {2001},
		publisher = {Election Commission of Malaysia},
	}

	@book{sarawak2006report,
		title     = {Report on the State Legislative Assembly General Election 2006 of the State of Sarawak},
		author    = {Election Commission},
		year      = {2006},
		publisher = {Election Commission of Malaysia},
	}

	@book{means1991malaysia,
		author    = {Gordon P. Means},
		title     = {Malaysia: The Second Generation},
		publisher = {Oxford University Press},
		address   = {Singapore},
		year      = {1991}
	}

	@article{yusoff2001sabah,
		title={Sabah politics under {Pairin}},
		author={Yusoff, Mohammad Agus},
		journal={JATI - Journal of Southeast Asian Studies},
		volume={6},
		pages={29--48},
		year={2001}
	}

	@article{lee2020collapse,
		title={The Collapse of the State Government in {Sabah}: Back to the Drawing Board},
		author={Lee, P.O.},
		journal={ISEAS - Yusof Ishak Institute Commentaries},
		year={2020},
		note={Available at: \url{https://citethis.link/meco1-iseas}}
	}

	@incollection{junid2019battle,
		title={The battle for {Perak}},
		author={Junid, Iskandar Dzulkarnain Ahmad},
		booktitle={Malaysia's 14th General Election and {UMNO}'s Fall},
		pages={223--239},
		year={2019},
		publisher={Routledge}
	}
\end{filecontents*}
